%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT 
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Java Developer/Support} % Job title
  {SPAC Information Technology Inc.} % Organization
  {Pasig, NCR, Philippines} % Location
  {Aug. 2022 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Resolve incidents and problem tickets as reported by the client team.}
      \item {Proactively manage the maintenance of the infrastructure/technology For Java}
      \item {Coordinate with cross-functional and cross-technical groups in the completion of maintenance or project activities.}
      \item {Apply configuration changes and required patches based on approved
      requirements and specifications.}
      \item {Implement provisioning requests as required by the client or based on
      project plans.}
      \item {Perform quality assurance activities for the technologies being managed.}
      \item {Apply client-specific methods and tools for carrying out any support or
      project deliverables \\}
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {NextIX Inc.} % Organization
    {Cebu, Philippines} % Location
    {Oct. 2018 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and deployed a native Java desktop application to the Microsoft Store.}
        \item {Developed an automated trading bot that is integrated with the APIs of multiple crypto exchanges using Laravel.}
        \item {Conducted market-making on multiple market pairs within several crypto exchanges.}
        \item {Collaborated with a Huawei sales/marketing representative on the configuration and integration of Huawei Cloud's Object Storage Solution.}
        \item {Built an API collection which analyzes, evaluates, and verifies user-submitted documents using Express.js, MongoDB, and Google Vision API.}
        \item {Integrated several third-party storage and payment solutions such as Dropbox, PayPal, and DragonPay using Laravel.}
        \item {Worked overseas with a foreign team on the Philippine Identification System's Iris and Face capture device API using C\#.}
        \item {Developed and deployed multiple ethereum smart contracts (ERC-721) to a third-party RPC provider using Solidity.}
        \item {Built APIs in a microservices architecture using Express.js and Quarkus, a Kubernetes native Java framework.}
        \item {Utilized Azure Key Vault for building APIs with database data encryption and decryption using Express.js, and Django REST}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
